Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-23 VMCAI-revised-version/final.tex
appendix minsky

We now delve into more details into the undecidability results 
upon which rely
Theorem~\ref{indec WSTS with dcs}
and
Theorem~\ref{srp down up},
namely, that
{\sc Resilience} and {\sc State-resilience} when $\Safe = \mathop{\downarrow}~\Safe$
are undecidable for Minsky machines
and 
for reset-VASS.

>>>>

We now delve into more details into the undecidability results 
upon which rely
Proposition~\ref{indec WSTS with dcs}
and
Proposition~\ref{srp down up},
namely, that
{\sc Resilience} and {\sc State-resilience} when $\Safe = \mathop{\downarrow}~\Safe$
are undecidable for Minsky machines
and 
for reset-VASS.
